Tabular Constraint Learning

### 2016-04-27 Paper/ECAI/tabular.tex
fixing introduction

\section{Introduction}
Millions of people across the world use spreadsheets everyday.
Yet, many people lack a complete understanding of the structures and existing dependencies in the data.
Indeed, the most useful part of spreadsheets is often the formulas and often these formula disappear when a file is exported and shared, for example as a CSV file.
This brings us to the question: can we discover or reconstruct structural relations in flat tabular spreadsheet data?
Moreover, can we accomplish this task in a general way that allows declarative specification of constraints to discover?

@@

\sergey{bullet points for Luc and Tias to rework introduction}\\
\textbf{Motivation}:
\samuel{Suggest better table layouts / formula translation}
\begin{itemize}
  \item File generated from model, model got lost, need to reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

@@

We consider various sets of cells in tables:
\begin{itemize}
  \item {\bf Cells}: Each entry in the matrix/table is called  a \textit{cell}.
  We use the notation $T[a,b]$ to refer to a particular cell in the table~$T$ at the row with index~$a$ and the column with index~$b$.
  \item {\bf Columns and rows}: To refer to the $a$-th row (column) we use the following syntax $T[a,{:}]$ ($T[{:},a]$), to refer to a subrange from $a$ to $b$ we use $T[a{:}b,]$ ($T[,a{:}b]$).
  \item
  A \textbf{vector} is either a column or a row that is type-consistent.
  If a vector is a row (column), we say that it has a \textit{row} (\textit{column}) orientation.
  \item
  A \textbf{group} is a subrange of vectors with the same orientation in a table.
  We use the following notation to refer to a row (column) group $G$ in a table $T$ with rows (columns) ranging from $a$ to $b$: $G = T[a{:}b,:]$ ($G = T[{:},a{:}b]$), where $a,b$ are natural numbers.
  The \textit{length} of a row (column) group $G$, written as \textit{length(G)}, is the number of its columns (rows); We call a group $G$ \textit{numeric} (\textit{textual}, etc), written as \textit{numeric(G)}, if all its vectors contain numeric (textual, etc) elements.
  \item
 A \textit{subgroup} $g$ is a subrange of vectors belonging to a group $G$. If the subgroup $g$ must contain only one vector, we write $g \in G$. %It defines what it means for a constraint to be well-formed
%We refer to a subgroup of a group $G$ in \groups as $g$. A \textit{subgroup} $g$ is a subrange of vectors in a group $G$. If a subgroup $g$ must contain only one vector, we write $g \in G$.
% A \textit{subgroup} $G'$ is a subrange of vectors belonging to a group $G$. If the subgroup $\{v\}$ must contain only one vector, we write $v \in G$.
\end{itemize}
%For notational convenience, we will refer to vectors in {\rm roman} and to groups in {\bf bold}. {\bf CHECK}

>>>>

\section{Introduction}
\sergey{Needs to be checked, bullet points for Luc and Tias to rework introduction}\\
Millions of people across the world use spreadsheets everyday.
Yet, many people lack a complete understanding of the structures and existing dependencies in the data.
Indeed, the most useful part of spreadsheets is often the formulas and often these formula disappear when a file is exported and shared, for example as a CSV file.
This brings us to the question: can we discover or reconstruct structural relations in flat tabular spreadsheet data?
Moreover, can we accomplish this task in a general way that allows declarative specification of constraints to discover?

@@

\textbf{Motivation}:
\samuel{Suggest better table layouts / formula translation}
\begin{itemize}
  \item File generated from model, model got lost, need to reconstruct
  \item Constraint programming is hard - is Excel hard?
  \item Avoid manual analysis, provide selection of constraints
  \item Error checking
  \item Completion, gain speed and insights (Complicated constraints, also complicated to verify, too much output)
\end{itemize}

@@

We consider various sets of cells in tables:
\begin{itemize}
  \item {\bf Cells}: Each entry in the matrix/table is called  a \textit{cell}.
  We use the notation $T[a,b]$ to refer to a particular cell in the table~$T$ at the row with index~$a$ and the column with index~$b$.
  \item {\bf Columns and rows}: To refer to the $a$-th row (column) we use the following syntax $T[a,{:}]$ ($T[{:},a]$), to refer to a subrange from $a$ to $b$ we use $T[a{:}b,]$ ($T[,a{:}b]$).
  \item
  A \textbf{vector} is either a column or a row that is type-consistent.
  If a vector is a row (column), we say that it has the \textit{row} (\textit{column}) orientation.
  \item
  A \textbf{group} is a subrange of vectors with the same orientation in a table.
  We use the following notation to refer to a row (column) group $G$ in a table $T$ with rows (columns) ranging from $a$ to $b$: $G = T[a{:}b,:]$ ($G = T[{:},a{:}b]$), where $a,b$ are natural numbers.
  The \textit{length} of a row (column) group $G$, written as \textit{length(G)}, is the number of its columns (rows); We call a group $G$ \textit{numeric} (\textit{textual}, etc), written as \textit{numeric(G)}, if all its vectors contain numeric (textual, etc) elements.
  \item
 A \textit{subgroup} $g$ is a subrange of vectors belonging to a group $G$. If the subgroup $g$ must contain only one vector, we write $g \in G$. %It defines what it means for a constraint to be well-formed
%We refer to a subgroup of a group $G$ in \groups as $g$. A \textit{subgroup} $g$ is a subrange of vectors in a group $G$. If a subgroup $g$ must contain only one vector, we write $g \in G$.
% A \textit{subgroup} $G'$ is a subrange of vectors belonging to a group $G$. If the subgroup $\{v\}$ must contain only one vector, we write $v \in G$.
\end{itemize}
%For notational convenience, we will refer to vectors in {\rm roman} and to groups in {\bf bold}. {\bf CHECK}
